---
title: "Meeting Minutes"
author: "Romeo Penheiro"
date: "24 June 2021"
output: html_document
---

In today's meeting, we decided to learn branching. Branching is essential when we are working on a new feature. It allows us to add a new feature in a branch, away from the main branch. Making changes and reviews by collaborators are also made easy through this process.

We also brainstormed some ideas for future posts. They are listed below:

- TIL: Today I Learned
- Our vision and/or mission og OpenCogSci
- Something related to graduate student life
- Tips and tricks in R
- Have a link to CM's website for RStats
- Make improvements to CM's course by making pull requests
- RP's ideas: can write on my personal experience in the course, add resources for advanced stats, contribute to chapter 14, and/or add an exmaple of data wrangling using untidy dataset. 

That's it. So, back to branching...

## Step 1: Get local repo up to speed

- Local repo will be syced with the remote repo

```{r include=TRUE, eval=FALSE}
git checkout main
git fetch origin
git reset --hard origin/main # This has an irreversible consequence where any unsaved commits will be deleted. We can instead use...
git rebase # This allows us to insert a commit within a tree of changes
```


## Step 3: Create a new branch

```{r include=TRUE, eval=FALSE}
git checkout -b test-branch # The printout will show that you have switched to a new branch 'test-branch'. So, this create a new branch AND switches you to the new branch
git branch # The printout will confirm that a new branch is created

```

## Step 4: Edit something in content

```{r include=TRUE, eval=FALSE}
ls
cd content
open About.md # Here RP changed the content of the post
git status # git status will show you what has been modified, staged, or committed. 
```

## Step 5: Commit the changes

```{r include=TRUE, eval=FALSE}
git add . # . represents everything in the directory
git status # Shows all the files that are new (not the ones in the git ignore). This is to make sure that we have all the right files in the commit. 
git commit -m "changed the about section" # We seal the current status with a short message
git status
git push -u origin test-branch 
```

## Step 6: Pull Request

- Go to GitHUB GUI (browser)
- In the `opensogsci` repo, you will have to click on the green button for `compare & pull request`
- Write a substantive summary of what were changed and click `pull request`
- Any comments left by collaborators will show up on the tab `Pull Requests`