---
title: "Meeting Minutes"
author: "Romeo Penheiro", "Chunyun Ma"
date: "27 October 2021"
output: html_document
---

```{r include=FALSE}
knitr::opts_chunk$set(
  comment = "",
  results = "hold"
  )
```

```{r packages, message = FALSE}
# Install xfun so that I can use xfun::pkg_load2
if (!requireNamespace('xfun')) install.packages('xfun')
cran_packages = c(
        "httr"
)

if (length(cran_packages) != 0) xfun::pkg_load2(cran_packages)
```

## Keywords and references

Get
: Retrieve whatever is specified by the URL

Post
: Create resource at URL with data in body

Put
: Update recluse at URL with data in body

Delete
: Delete resource at URL

`JSON`
: collection of key-value pairs

toJSON
: takes a R list and turns it in to a JSON file

fromJSON
: takes a JSON file and turns it in to an R list

Status code
: <http://http.cats>

## Example snippets

### Get the data

```{r}
# Optionally, adding a header in the json format
receive <- httr::GET(
  "http://httpbin.org/get",
  httr::add_headers(Name = "Romeo")
)
receive
```

### Publish data on server

```{r}
url <- "http://httpbin.org/post"
body <- list(a = 1, b = 2, c =3)

publish <- httr::POST(url, body = body, encode = "form")
publish
## Other examples
# publish <- httr::POST(url, body = body, encode = "multipart")
# publish <- httr::POST(url, body = body, encode = "raw")
# publish <- httr::POST(url, body = body, encode = "json")
```

### Parsing received data

#### Status code {-}

```{r}
receive$status_code
```

Human understandable:

```{r}
httr::http_status(receive) 
```


Program defensively with the following functions
to warn when status code is not 200

<!-- Don't evaluate the next chunk, or this rmarkdown file will not knit. -->

```{r eval=FALSE}
receive2 <- receive
receive2$status_code <- 404
httr::warn_for_status(receive2)
httr::stop_for_status(receive2)
```

#### Headers {-}

```{r}
httr::headers(receive)
```

Extract server

```{r}
httr::headers(receive)$server
```

#### Content body of received data {-}

By default, the content will be binary.

```{r}
receive$content

# equivalent to
# httr::content(receive, "raw")
```

Helper function `httr::content()` helps to parse the contents of the body
if set type of content to `parse`.
Other options for type includes `raw` (default) and `text.`

```{r}
frozen <- httr::GET("http://www.omdbapi.com/?t=frozen")
details <- httr::content(frozen, "parse")
details$Error
```

