---
title: "Meeting Minutes"
author: "Romeo Penheiro"
date: "28 June 2021"
output: html_document
---

In today's meeting, we picked up from where we left off at the last meeting. Check out the meeting minutes to verify what was done. Today, we will continue from Step 8 and merge `test-branch` and `cool-branch`. We will also create a new branch `notes` for meeting minutes.

## Step 8: Collaborator reviews and accepts the changes

- Here, RP is going to review TS's changes (This section is a work in progress. Please check the next meeting minutes to check what was done.)

```{r include=TRUE, eval=FALSE}
git branch -a # Green: local, Red: remote
git fetch -a # Same as git fetch origin
git pull

# To see the difference use any of the following commands
git diff c6870e2a844d2b15668906dd826ab94c437824c9..412529e833cd0b8482fd24f399969f44d33477c1 
git diff c6870e2a844d2b15668906dd826ab94c437824c9..412529e833cd0b8482fd24f399969f44d33477c1 --content/about.md 
git diff c6870e2..412529e

```

## Step 9: Edit something in content

```{r include=TRUE, eval=FALSE}
open About.md # RP uses TextEditor
# Added an empty final line
git status # git status will show you what has been modified, staged, or committed. 
```
Note: you can use `control + c` to kill a process

Why is it important to add an empty line at the end of the line?

It could be something to do with convention and/or compatibility of files among Windows/MAC users. RP did a quick search to find out what it is about - didn't find anything.

## Step 10: Commit and push the changes

```{r include=TRUE, eval=FALSE}
git add .
git commit -m "<add a commit message>"
git log # to see the history of git commits, all commits in the test branch, check out below all the recipes

git branch # to see local branches and which one I am on
git branch -a # to see above + local repo's understanding of the branches that exist in the remote repo
git branch -vv # to see local branches + most recent commits

git push # Don't have to mention -u test-branch, because tracking branch has already been established in the past. 
```

* https://github.com/jmmendivil/git-log-recipes

## Step 11: Merge the branches

```{r include=TRUE, eval=FALSE}
git checkout main # Or git switch main
git pull # This is to sync with the remote repo (test-branch)
git pull origin test-branch # This is to consolidated the final version of test branch and then merge to the main branch
git push # Step to perform the merge to the remote repo. The steps before this were done locally. If the pull request is successfully merged and closed, you will see it in GitHub GUI browser.

```


Next, RP made changes to `cool-branch` for TS to checkout and merge. This are the same steps as those from the last meeting (you can find the notes under Step 4. They have been added before for ease of reading).

## Step 12: Synch the local repo

Before the edit, RP had to update the local repo with the remote `cool-branch` repo

```{r include=TRUE, eval=FALSE}
git branch -a # Green: local, Red: remote; This step is to check what branch HEAD of local repo is on and if we need to switch. The printout will give a list of branches that the local repo currently has.
git fetch --all 
git branch -a # Prints all the branches, both local and remote
git checkout cool-branch

```

## Step 13: Edit something in content in `cool-branch`


```{r include=TRUE, eval=FALSE}
ls
cd content
nvim About.md # We actually decided NOT to carry out this step as RP had made changes here in his 'test-branch'. Instead, TS used...
nvim Lorem Ipsum # There were some tech issues on TS's side. He had to use control + c to toggle between save and edit mode on nvim. Usually, esc can be used to exit the text editor, but he wasn't able to use it because Zoom shreen sharing service had a tech issue. *
git status # git status will show you what has been modified, staged, or committed. 

open <filename> # It was a boiler-plate post
# Deleted all the latin in the post and added some blank lines at the end of the file
git status # git status will show you what has been modified, staged, or committed.

```

## Step 14: Commit and push the changes

```{r include=TRUE, eval=FALSE}
git add .
git commit -m "<add a commit message>"
git log # to see the history of git commits, all commits in the test branch, check out below all the recipes
git branch -a # or...
git branch -vv # to see where I am
git push # Don't have to mention -u cool-branch
```

Next TS repeated steps 8-11 to practice reviewing edits and merging on the terminal.

Notes:

- We don't have to navigate to the directory to work with git. We can use relative paths to refer to files.
- You can use hjkl instead of arrow keys: https://catonmat.net/why-vim-uses-hjkl-as-arrow-keys
- In a future lesson, we will have to delete R folder in the main branch
- We will be meeting on Google Meets from now on
- Try to be critical of the explanation from CM

# Adding a new branch for our meeting minutes

Resource: https://bookdown.org/yihui/blogdown/configuration.html#options (section: `ignoreFiles`)


## Create a new branch `notes`

```{r include=TRUE, eval=FALSE}
git checkout -b notes # The printout will show that you have switched to a new branch 'notes'
git status

```

## Add `notes` to config.yaml

```{r include=TRUE, eval=FALSE}
open .config.yaml
# append the following line 
 - notes$ # $ indicates end of the name
# Save and close the file
        
```


## Make a new dir called `notes`

```{r include=TRUE, eval=FALSE}
mkdir notes
        
```

## Move minutes to `notes` and renaming

```{r include=TRUE, eval=FALSE}
mv <file path> a notes/

        
mv <file path> # changing the name
stat <new file name> # this shows metadata relating to a particular file's history. Can be useful for example figuring out when a file was created.  
        
```

Note: the files will be named in the following convention minutes_YYYY-MM-DD

## An accidental reset

```{r include=TRUE, eval=FALSE}
We unstage everything 
git reset # We accidentally unstaged everything and the changes we made were no longer tracked. The printout shows was unstaged and here we noticed that the notes directory was not there so we did a ...
git status # we realized it was untracked. Reset unstaged everything, even the creation of notes dir, and the files inside. So we had to do atomic commits.

```


## Atomic stage, commit, and pull

```{r include=TRUE, eval=FALSE}
git add config.yaml # atomic commit
git commit -m "added the notes folder to .ignorefiles"
git add notes/
git commit -m "added a notes folder and minutes inside"
git push -u origin notes 
```

